Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-24 src/7.C++.tex
Minor fix

Another important reason that Kokkos is an ideal choice for an eduactional setting is the feedback cycle it participates in with the ISO-C++ language standard itself.  Over the past decade or so, work on the Kokkos programming model has contributed to a number of current or near-future ISO-C++ features, including \code{atomic_ref}, \code{mdspan}, and executors.  This interplay between Kokkos and the C++ standard means that students using the model will be exposed to paradigms that will likely be part of the broader standard C++ ecosystem, thus preparing them for a much wider range of application areas.

>>>>

Another important reason that Kokkos is an ideal choice for an eduactional setting is the feedback cycle it participates in with the ISO-C++ language standard itself.  Over the past decade or so, work on the Kokkos programming model has contributed to a number of current or near-future ISO-C++ features, including \emph{atomic\_ref}, \emph{mdspan}, and executors.  This interplay between Kokkos and the C++ standard means that students using the model will be exposed to paradigms that will likely be part of the broader standard C++ ecosystem, thus preparing them for a much wider range of application areas.
